### 2018-08-08 Sections/protocols_for_the_quantum_internet.tex
Indexing

However, these states are notoriously difficult and technologically challenging to prepare, and can only be prepared non-deterministically using linear optics \cite{bib:Cable07}. If a remote server had the capacity to prepare such states, they would be in high demand across the globe. Hindering this, NOON states are very fragile creatures. First, they exhibit exponentially increased susceptibility to loss -- loss of just a single photon completely decoheres the state, rendering it useless for metrological purposes. Second, the large photon-number, $N$, amplifies unwanted dephasing by a factor of $N$, as discussed in Sec.~\ref{sec:dephasing_error}. These considerations can be readily accommodated for in the QTCP protocol by tracking dephasing and loss metrics of the packets encapsulating the NOON states.

@@

\subsection{W-states}\index{W-states}

Using linear optics, W-states are amongst the most trivial entangled states to prepare. An $N$-mode W-state can be prepared directly using $N$ beamsplitters in a linear cascade, as shown in Fig.~\ref{fig:W_state_LO_prep}, where the beamsplitter reflectivities are chosen so as to create the uniform superposition, given by the pattern,
\begin{align}
	1-{\eta_1}^2 &= \frac{1}{N},\nonumber\\
	{\eta_1}^2 {\eta_2}^2 &= \frac{1}{N},\nonumber\\
	{\eta_1}^2 {\eta_3}^2 (1-{\eta_2}^2)  &= \frac{1}{N},\nonumber\\
	{\eta_1}^2 {\eta_4}^2(1-{\eta_2}^2) (1-{\eta_3}^2)  &= \frac{1}{N},\nonumber\\
	{\eta_1}^2 {\eta_i}^2 \prod_{j=2}^{i-1} (1-{\eta_j}^2) &= \frac{1}{N},\nonumber\\
	{\eta_N}^2 &= 1.
\end{align}

\begin{figure}[!htb]
\includegraphics[width=0.2\textwidth]{W_state_LO_prep}
\caption{Preparation of an $N$-mode W-state using a linear cascade of beamsplitters and a single-photon source.}\label{fig:W_state_LO_prep}	
\end{figure}

@@

However, it must be cautioned that cat states decohere very readily, since their well-defined parity implies decoherence upon loss of just a single photon. This makes QoS considerations particularly pertinent.

@@

Of particular interest to metrology\index{Quantum metrology} and CV quantum computing\index{Continuous-variable quantum computing} in particular, are squeezed states, states which have been longitudinally distorted in phase-space. In the metrological context, squeezed states enable sub-shotnoise limited metrology \cite{???}, thereby outperforming any classical protocol, using, for example, coherent states.

@@

\begin{figure}[htpb]
\includegraphics[width=0.35\textwidth]{detector_multiplexing}
\caption{Multiplexed number-resolved photo-detection using non-number-resolved photo-detectors. The principle is to spread out (as uniformly as possible) a multi-photon state across a large number of modes, sufficiently large that it is unlikely that more than one photon will be present in any given mode. Then, the sum of the number of clicks at each mode closely approximates the incident photon-number. (a) In the spatial domain. (b) In the temporal domain. The advantage of employing the temporally multiplexed architecture is that only a single detector is required, unlike the multiple independent detectors required in the spatially multiplexed scheme. However this requires that the dead-time\index{Dead-time} of the detector is less than the round-trip time of the fibre loop. An alternate, but conceptually equivalent approach is to spatially disperse the optical field across a charge-coupled device (CCD)\index{Charge-coupled device}, much like that found in a regular digital camera, except with single-photon resolution per-pixel. This achieves an effectively very large number of optical modes.} \label{fig:det_mult}
\end{figure}

@@

Experimentally, there have been several demonstrations of the protocol, albeit at relatively short distances. Continuous time-bin\index{Time-bin encoding} entangled photons were used as the entanglement resource to obtain a time-correlation between a distance of 3km \cite{bib:valencia2004distant}, and another technique based on Hong-Ou-Mandel interferometry\index{Hong-Ou-Mandel interferometry} was performed across a 4km fibre link \cite{bib:quan2016demonstration}. Several other demonstrations based on nuclear magnetic resonance (NMR)\index{Nuclear magnetic resonance} \cite{bib:zhang2004nuclear, bib:kong2017implementation} have also been performed.

>>>>

However, these states are notoriously difficult and technologically challenging to prepare, and can only be prepared non-deterministically using linear optics \cite{bib:Cable07, bib:PhysRevA.65.030101, bib:PhysRevA.76.063808}. If a remote server had the capacity to prepare such states, they would be in high demand across the globe. Hindering this, NOON states are very fragile creatures. First, they exhibit exponentially increased susceptibility to loss -- loss of just a single photon completely decoheres the state, rendering it useless for metrological purposes. Second, the large photon-number, $N$, amplifies unwanted dephasing by a factor of $N$, as discussed in Sec.~\ref{sec:dephasing_error}. These considerations can be readily accommodated for in the QTCP protocol by tracking dephasing and loss metrics of the packets encapsulating the NOON states.

@@

\subsection{W-states}\index{W-states}\label{sec:W_state_prep}

W-states are a class of non-maximally-entangled states across an arbitrary number of qubits/modes. They are given by the equal superposition of a single excitation/`1' across all $n$ qubits. Thus, there are $n$ terms in the superposition, of the form,
\begin{align}
\ket\psi_\mathrm{W}^{(n)} &= \frac{1}{\sqrt{n}} \sum_{i=1}^n \hat{a}_i^\dag \ket{0}^{\otimes n}\nonumber\\
&= \frac{1}{\sqrt{n}}(\ket{1,0,0,0,\dots} + \ket{0,1,0,0,\dots}\nonumber\\
&+ \ket{0,0,1,0,\dots} + \ket{0,0,0,1,\dots} + \dots).
\end{align}

W-states are a class of states distinct from GHZ states (for any \mbox{$n\geq 3$}). Unlike GHZ states, W-states preserve some entanglement when a single qubit is traced out of the system, giving them a degree of robustness against qubit loss. This property is discussed in further detail in Secs.~\ref{sec:atomic_ens} \& \ref{sec:error_averaging}, where this property is exploited for error correction purposes.

Using linear optics, W-states are amongst the most trivial entangled states to prepare, using a simple fanout operation. An $n$-mode W-state can be prepared directly using $n$ beamsplitters in a linear cascade, as shown in Fig.~\ref{fig:W_state_LO_prep}, where the beamsplitter reflectivities are chosen so as to create the uniform superposition, given by the pattern,
\begin{align}
	{\eta_1}^2 &= 1 - \frac{1}{n},\nonumber\\
	{\eta_1}^2 {\eta_2}^2 &= \frac{1}{n},\nonumber\\
	{\eta_1}^2 {\eta_3}^2 (1-{\eta_2}^2)  &= \frac{1}{n},\nonumber\\
	{\eta_1}^2 {\eta_4}^2(1-{\eta_2}^2) (1-{\eta_3}^2)  &= \frac{1}{n},\nonumber\\
	{\eta_1}^2 {\eta_i}^2 \prod_{j=2}^{i-1} (1-{\eta_j}^2) &= \frac{1}{n},\nonumber\\
	{\eta_n}^2 &= 1.
\end{align}

\begin{figure}[!htb]
\includegraphics[width=0.2\textwidth]{W_state_LO_prep}
\caption{Preparation of an $n$-mode W-state using a linear cascade of beamsplitters and a single-photon source.}\label{fig:W_state_LO_prep}	
\end{figure}

Alternately, an entire basis of W-states\footnote{We refer to a `basis' of W-states as being a set of states that are all equivalent to a standard W-state up to local phases.} is accessible using linear optics networks described by unitaries where all matrix elements have amplitude $1/\sqrt{n}$, differing only via local phases. This includes the generalised Hadamard transform\index{Hadamard transform}, and quantum Fourier transform\index{Quantum Fourier transform}.

@@

However, it must be cautioned that cat states decohere very readily, since their well-defined parity implies decoherence upon loss or measurement of just a single photon. This makes QoS considerations particularly pertinent.

@@

Of particular interest to metrology\index{Quantum metrology} and CV quantum computing\index{Continuous-variable quantum computation} in particular, are squeezed states, states which have been longitudinally distorted in phase-space. In the metrological context, squeezed states enable sub-shotnoise limited metrology \cite{???}, thereby outperforming any classical protocol, using, for example, coherent states.

@@

\begin{figure}[htpb]
\includegraphics[width=0.35\textwidth]{detector_multiplexing}
\caption{Multiplexed number-resolved photo-detection using non-number-resolved photo-detectors. The principle is to spread out (as uniformly as possible) a multi-photon state across a large number of modes, sufficiently large that it is unlikely that more than one photon will be present in any given mode. Then, the sum of the number of clicks at each mode closely approximates the incident photon-number. (a) In the spatial domain. (b) In the temporal domain. The advantage of employing the temporally multiplexed architecture is that only a single detector is required, unlike the multiple independent detectors required in the spatially multiplexed scheme. However this requires that the dead-time\index{Dead-time} of the detector is less than the round-trip time of the fibre loop. An alternate, but conceptually equivalent approach is to spatially disperse the optical field across a charge-coupled device (CCD)\index{Charge-coupled device (CCD)}, much like that found in a regular digital camera, except with single-photon resolution per-pixel. This achieves an effectively very large number of optical modes.} \label{fig:det_mult}
\end{figure}

@@

Experimentally, there have been several demonstrations of the protocol, albeit at relatively short distances. Continuous time-bin\index{Time-bin encoding} entangled photons were used as the entanglement resource to obtain a time-correlation between a distance of 3km \cite{bib:valencia2004distant}, and another technique based on Hong-Ou-Mandel interferometry\index{Hong-Ou-Mandel (HOM) interferometry} was performed across a 4km fibre link \cite{bib:quan2016demonstration}. Several other demonstrations based on nuclear magnetic resonance (NMR)\index{Nuclear magnetic resonance} \cite{bib:zhang2004nuclear, bib:kong2017implementation} have also been performed.

### 2018-08-08 Sections/quality_of_service.tex
floats
Indexing

Different error correcting codes have different error correcting power, and different resource overheads, which must be taken into consideration. The appropriate choice of code will largely be determined by the final \textsc{Services \& Applications} layer. For some simple quantum communications protocols, simple error correction (or even no error correction) may suffice. A full-fledged quantum computation on the other hand will require error rates within a fault-tolerance threshold\index{Fault-tolerance threshold}.

@@

The purification process $\mathcal{E}_\mathrm{purif}$ is realised very simply by Alice and Bob both performing parity measurements\index{Bell measurement} on their two qubits, whose measurement outcomes indicate whether the two qubits were equal ($+$) or different ($-$) -- their parity. These are easily implemented using CNOT gates, using the construction shown in Fig.~\ref{fig:parity_meas}, which implement the projectors,
\begin{align}\index{Parity measurement}\index{Parity projectors}
\hat\Pi^+ &= \ket{0,0}\bra{0,0} + \ket{1,1}\bra{1,1}, \nonumber \\
\hat\Pi^- &= \ket{0,1}\bra{0,1} + \ket{1,0}\bra{1,0}.
\end{align}

@@

\begin{figure}[!htb]
	\begin{align}
		\Qcircuit @C=.7em @R=.4em @! {
		\lstick{} & \qw & \targ & \meter \\
		\lstick{} & \qw & \ctrl{-1} & \qw
		} \nonumber
	\end{align}
	\caption{Construction of a parity measurement circuit using a single CNOT gate and a single-qubit measurement. The measurement outcome indicates whether the two input qubits were the same (\mbox{$\ket{0}\ket{0}$}, \mbox{$\ket{1}\ket{1}$}) or different (\mbox{$\ket{0}\ket{1}$}, \mbox{$\ket{1}\ket{0}$}). See Sec.~\ref{sec:bell_proj} for a simple linear optics construction for this operation.}\label{fig:parity_meas}\index{Parity measurement}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.39\textwidth]{entanglement_purification}
\caption{Protocol for entanglement purification of two noisy Bell pairs (blue) into a single less noisy Bell pair. Not shown are trivial single-qubit local corrections that may need to be made, depending upon measurement outcomes.} \label{fig:ent_purif_circ}\index{Entanglement purification protocol}
\end{figure}

@@

\begin{table}[!htb]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function ThreeQubitCode($\ket\psi$):
\begin{enumerate}
\item Using two CNOT gates, redundantly encode the logical single-qubit state,
\begin{align}
\ket\psi=\alpha\ket{0}+\beta\ket{1},
\end{align}
into the 3-qubit state,
\begin{align}
\ket\psi_R &= \hat{\mathrm{CNOT}}_{1,2}\hat{\mathrm{CNOT}}_{1,3}\ket\psi\ket{00} \nonumber \\
&= \alpha\ket{000}+\beta\ket{111}.
\end{align}
\item Independently apply bit-flip channels $\mathcal{E}_X$ to each of the three encoded qubits.
\item If exactly one bit-flip operation was applied in total, the three possible erroneous encoded states are,
\begin{align}
\ket\psi_1 &= \hat{X}_1 \ket\psi_R = \alpha\ket{001}+\beta\ket{110}, \nonumber \\
\ket\psi_2 &= \hat{X}_2 \ket\psi_R = \alpha\ket{010}+\beta\ket{101}, \nonumber \\
\ket\psi_3 &= \hat{X}_3 \ket\psi_R = \alpha\ket{100}+\beta\ket{011}.
\end{align}
\item Determine the parity of each of the three pairs of encoded qubits.
\item Assuming at most a single bit-flip operation has occurred on the encoded state, the three parity outcomes uniquely determine which encoded qubit the bit-flip was applied to.
\item Apply classically-controlled bit-flip recovery operations, $\mathcal{R}$, to correct the encoded state, recovering $\ket\psi_R$.
\item Apply the inverse of the encoding operation to recover $\ket\psi$.
\item $\Box$
\end{enumerate}}
\begin{align}
\Qcircuit @C=1.3em @R=.6em {
  & \lstick{\ket{\psi}} & \ctrl{2} & \gate{\mathcal{E}_X}  & \qw & \qw              & \ctrl{3}  & \qw       & \ctrl{4} & \qw & \multigate{2}{\ \mathcal{R}\ } & \qw \\
  & \lstick{\ket{0}}    & \targ    & \gate{\mathcal{E}_X}  & \qw & \qw              & \ctrl{2}  & \ctrl{2}  & \qw      & \qw & \ghost{\ \mathcal{R}\ } \qw & \qw \\
  & \lstick{\ket{0}}    & \targ    & \gate{\mathcal{E}_X}  & \qw & \qw              & \qw       & \ctrl{2}  & \ctrl{3} & \qw & \ghost{\ \mathcal{R}\ } \qw & \qw \\
  &          &          &          & & \lstick{\ket{0}} & \targ \qw & \qw       & \qw      & \meter & \control \cw \cwx \\
  &          &          &          & & \lstick{\ket{0}} & \qw       & \targ \qw & \qw      & \meter & \control \cw \cwx \\
  &          &          &          & & \lstick{\ket{0}} & \qw       & \qw       & \targ    & \meter & \control \cw \cwx
} \nonumber
\end{align}
\end{mdframed}
\caption{3-qubit code for protecting against at most a single logical bit-flip error. The doubly-controlled CNOT gates represent parity measurements, \mbox{$n_3=n_1\oplus n_2$}, where $n_i$ represents the value of the $i$th qubit. In a Hadamard-rotated basis, the same circuit may be employed to protect against a single phase-flip error. And by concatenating the two we obtain a 9-qubit code protecting against a single depolarising error (i.e joint bit-flip/phase-flip), which is a universal single-qubit error model.} \label{alg:three_QEC}
\end{table}

@@

Importantly, topological codes do not require joint measurements across the entire graph state, instead requiring only operations localised to small regions within the graph. Thanks to this, computation using such topological codes can remain distributed\index{Distributed computation} without requiring the entire state to be held locally by a particular host, or requiring full access to the entire state by any particular user. As with cluster states, a large graph can be stitched together from a patchwork of smaller neighbouring graphs.

@@

\begin{figure*}[!htb]
	\includegraphics[width=0.47\textwidth]{torus}
	\includegraphics[width=0.47\textwidth]{toric_code}
	\caption{Graph representation of the toric QEC code, and its associated stabilisers. The graph resides on a torus (left), while the physical qubits reside on the embedded lattice (right). The star and plaquette stabilisers across all vertices, jointly specify the state of the graph up to two missing degrees of freedom, which encode a single logical qubit. Thus, a logical qubit is encoded jointly across the entire graph, not at any specific vertex. Logical operations are performed via operations following topological paths through the lattice (not shown). The graph may be distributed across multiple hosts for distributed quantum computation.} \label{fig:toric_code}
\end{figure*}

@@

\begin{figure}[!htb]
	\includegraphics[width=0.3\textwidth]{toric_code_correction}
	\caption{QEC of a single bit-flip (top) and phase-flip (bottom) error via measuring two overlapping stabilisers. If there is at most one bit- or phase-flip error, as per this graphic, then upon measuring all the star and plaquette stabilisers, only those whose qubits are affected by the error channel will yield the $-1$ measurement outcome, the others all yielding $+1$. Such an error will affect exactly two stabilisers, whose qubit in common must have been the one affected by the respective error, which can subsequently be corrected since the type of the error and its location are known. Thus, in this example, all of the $\hat{S}_+^{(1)}$, $\hat{S}_+^{(2)}$, $\hat{S}_\square^{(1)}$ and $\hat{S}_\square^{(2)}$ stabilisers will yield $-1$ outcomes for the shown $\hat{X}$ and $\hat{Z}$ errors, whereas any of the remaining (not shown) $\hat{S}_k^{(j)}$ will yield $+1$ outcomes, which uniquely specifies where those errors took place.}\label{fig:toric_corr}	
\end{figure}

@@

\begin{figure}[!htb]
	\includegraphics[width=0.47\textwidth]{torus_paulis}
	\caption{Implementation of logical Pauli-$\hat{X}$ (\comment{which colour?}) and -$\hat{Z}$ (\comment{which colour?}) operations on a toric code qubit via the application of a chain of local Paulis. The chains must circumnavigate the torus around either axis. Any path topologically equivalent to such a circumnavigation of the torus is sufficient, enabling paths to bypass defects in the lattice.} \label{fig:toric_code_paulis}
\end{figure}

@@

Aside from the \textit{active} QoS techniques discussed until now, there is also a recently described \textit{passive} technique that requires no feedforward to operate. This technique, called \textit{unitary error averaging}, is formulated specifically in the linear optical context. It is an open question whether it generalises to other models, such as conventional quantum circuits.

@@

\cite{MarshmanLundRohdeRalph} showed that by using an optical fanout operation, which splits a set of optical modes equally across multiple sets of modes in a type of redundant encoding, and passing each set through an independently manufactured copy of the imperfect unitary, $\tilde{U}_i$, upon post-selection on detecting all photons in the desired output modes, the output state will behave as if it had evolved through a network given by the arithmetic average of each of the imperfect copies of $\hat{U}_\mathrm{target}$,
\begin{align}
\hat{U}_\mathrm{av} = \frac{1}{M}\sum_{i=1}^M \tilde{U}_i.	
\end{align}
A schematic for the optical circuit is shown in Fig.~\ref{fig:error_av_circuit}.

\begin{figure}[!htb]
\includegraphics[width=0.47\textwidth]{unitary_error_averaging}
\caption{Protocol for error correction via unitary error averaging. Here our computation resides across \mbox{$N=2$} modes, and there are \mbox{$M=2$} redundant copies of the manufactured unitary, which straightforwardly generalises to arbitrary $M$ and $N$. A fanout operation splits the wave amplitudes from the set of $N$ input modes uniformly across $M$ sets of $N$ modes. Each set of $N$ evolves through an independent copy of the manufactured imperfect unitary, $\tilde{U}_i$. A reverse fanout operation recollects the bundles of modes. Upon post-selecting upon detecting all photons within the first $N$ modes, and none in the other ancillary modes, the state is projected into the subspace as if it had been acted upon by the arithmetic average of the imperfect unitaries.} \label{fig:error_av_circuit}	
\end{figure}

Note that the protocol doesn't require that the $M$ instances of the unitary be held locally. They operate independently in parallel and could therefore be distributed, with the independent copies held by entirely different parties in distant locations.\index{Distributed computation}\index{Parallelisation}

The protocol is necessarily non-deterministic, since sometimes photons will be measured in the error modes, signalling that the output state has been projected onto an erroneous subspace. However, when post-selection succeeds we have effectively evolved via the averaged operator, which statistically ought to more closely approximate $\hat{U}_\mathrm{target}$ than the individual $\tilde{U}_i$.

@@

\begin{figure*}[!htb]
\includegraphics[width=\textwidth]{bloch_sphere_dyn_dec}
\caption{Bloch sphere representation of a sequence to dynamically decouple an unknown $\hat{Z}$ rotation from a qubit. (a) Blue dot represents the initial state. (b) The state undergoes an unknown $\hat{Z}(\theta)$ rotation. (c) A bit-flip ($\hat{X}$) flips the Bloch sphere upside down. (d) Waiting for the same time as before such that the same unknown $\hat{Z}$-rotation takes place, the state ends up in its initial state, independent of the $\hat{Z}$-rotation angle $\theta$, but assuming it was the same on both occasions in (b) and (d).} \label{fig:bloch_sphere_dyn_dec}	
\end{figure*}

>>>>

Different error correcting codes have different error correcting power, and different resource overheads, which must be taken into consideration. The appropriate choice of code will largely be determined by the final \textsc{Services \& Applications} layer. For some simple quantum communications protocols, simple error correction (or even no error correction) may suffice. A full-fledged quantum computation on the other hand will require error rates within a fault-tolerance threshold\index{Fault-tolerance thresholds}.

@@

The purification process $\mathcal{E}_\mathrm{purif}$ is realised very simply by Alice and Bob both performing parity measurements\index{Bell measurements} on their two qubits, whose measurement outcomes indicate whether the two qubits were equal ($+$) or different ($-$) -- their parity. These are easily implemented using CNOT gates, using the construction shown in Fig.~\ref{fig:parity_meas}, which implement the projectors,
\begin{align}\index{Parity measurement}\index{Parity projectors}
\hat\Pi^+ &= \ket{0,0}\bra{0,0} + \ket{1,1}\bra{1,1}, \nonumber \\
\hat\Pi^- &= \ket{0,1}\bra{0,1} + \ket{1,0}\bra{1,0}.
\end{align}

@@

\begin{figure}[htpb]
	\begin{align}
		\Qcircuit @C=.7em @R=.4em @! {
		\lstick{} & \qw & \targ & \meter \\
		\lstick{} & \qw & \ctrl{-1} & \qw
		} \nonumber
	\end{align}
	\caption{Construction of a parity measurement circuit using a single CNOT gate and a single-qubit measurement. The measurement outcome indicates whether the two input qubits were the same (\mbox{$\ket{0}\ket{0}$}, \mbox{$\ket{1}\ket{1}$}) or different (\mbox{$\ket{0}\ket{1}$}, \mbox{$\ket{1}\ket{0}$}). See Sec.~\ref{sec:bell_proj} for a simple linear optics construction for this operation.}\label{fig:parity_meas}\index{Parity measurement}
\end{figure}

@@

\begin{figure}[htpb]
\includegraphics[width=0.39\textwidth]{entanglement_purification}
\caption{Protocol for entanglement purification of two noisy Bell pairs (blue) into a single less noisy Bell pair. Not shown are trivial single-qubit local corrections that may need to be made, depending upon measurement outcomes.} \label{fig:ent_purif_circ}\index{Entanglement purification protocol}
\end{figure}

@@

\begin{table}[htpb]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function ThreeQubitCode($\ket\psi$):
\begin{enumerate}
\item Using two CNOT gates, redundantly encode the logical single-qubit state,
\begin{align}
\ket\psi=\alpha\ket{0}+\beta\ket{1},
\end{align}
into the 3-qubit state,
\begin{align}
\ket\psi_R &= \hat{\mathrm{CNOT}}_{1,2}\hat{\mathrm{CNOT}}_{1,3}\ket\psi\ket{00} \nonumber \\
&= \alpha\ket{000}+\beta\ket{111}.
\end{align}
\item Independently apply bit-flip channels $\mathcal{E}_X$ to each of the three encoded qubits.
\item If exactly one bit-flip operation was applied in total, the three possible erroneous encoded states are,
\begin{align}
\ket\psi_1 &= \hat{X}_1 \ket\psi_R = \alpha\ket{001}+\beta\ket{110}, \nonumber \\
\ket\psi_2 &= \hat{X}_2 \ket\psi_R = \alpha\ket{010}+\beta\ket{101}, \nonumber \\
\ket\psi_3 &= \hat{X}_3 \ket\psi_R = \alpha\ket{100}+\beta\ket{011}.
\end{align}
\item Determine the parity of each of the three pairs of encoded qubits.
\item Assuming at most a single bit-flip operation has occurred on the encoded state, the three parity outcomes uniquely determine which encoded qubit the bit-flip was applied to.
\item Apply classically-controlled bit-flip recovery operations, $\mathcal{R}$, to correct the encoded state, recovering $\ket\psi_R$.
\item Apply the inverse of the encoding operation to recover $\ket\psi$.
\item $\Box$
\end{enumerate}}
\begin{align}
\Qcircuit @C=1.3em @R=.6em {
  & \lstick{\ket{\psi}} & \ctrl{2} & \gate{\mathcal{E}_X}  & \qw & \qw              & \ctrl{3}  & \qw       & \ctrl{4} & \qw & \multigate{2}{\ \mathcal{R}\ } & \qw \\
  & \lstick{\ket{0}}    & \targ    & \gate{\mathcal{E}_X}  & \qw & \qw              & \ctrl{2}  & \ctrl{2}  & \qw      & \qw & \ghost{\ \mathcal{R}\ } \qw & \qw \\
  & \lstick{\ket{0}}    & \targ    & \gate{\mathcal{E}_X}  & \qw & \qw              & \qw       & \ctrl{2}  & \ctrl{3} & \qw & \ghost{\ \mathcal{R}\ } \qw & \qw \\
  &          &          &          & & \lstick{\ket{0}} & \targ \qw & \qw       & \qw      & \meter & \control \cw \cwx \\
  &          &          &          & & \lstick{\ket{0}} & \qw       & \targ \qw & \qw      & \meter & \control \cw \cwx \\
  &          &          &          & & \lstick{\ket{0}} & \qw       & \qw       & \targ    & \meter & \control \cw \cwx
} \nonumber
\end{align}
\end{mdframed}
\caption{3-qubit code for protecting against at most a single logical bit-flip error. The doubly-controlled CNOT gates represent parity measurements, \mbox{$n_3=n_1\oplus n_2$}, where $n_i$ represents the value of the $i$th qubit. In a Hadamard-rotated basis, the same circuit may be employed to protect against a single phase-flip error. And by concatenating the two we obtain a 9-qubit code protecting against a single depolarising error (i.e joint bit-flip/phase-flip), which is a universal single-qubit error model.} \label{alg:three_QEC}
\end{table}

@@

Importantly, topological codes do not require joint measurements across the entire graph state, instead requiring only operations localised to small regions within the graph. Thanks to this, computation using such topological codes can remain distributed\index{Distributed quantum computation} without requiring the entire state to be held locally by a particular host, or requiring full access to the entire state by any particular user. As with cluster states, a large graph can be stitched together from a patchwork of smaller neighbouring graphs.

@@

\begin{figure*}[htpb]
	\includegraphics[width=0.47\textwidth]{torus}
	\includegraphics[width=0.47\textwidth]{toric_code}
	\caption{Graph representation of the toric QEC code, and its associated stabilisers. The graph resides on a torus (left), while the physical qubits reside on the embedded lattice (right). The star and plaquette stabilisers across all vertices, jointly specify the state of the graph up to two missing degrees of freedom, which encode a single logical qubit. Thus, a logical qubit is encoded jointly across the entire graph, not at any specific vertex. Logical operations are performed via operations following topological paths through the lattice (not shown). The graph may be distributed across multiple hosts for distributed quantum computation.} \label{fig:toric_code}
\end{figure*}

@@

\begin{figure}[htpb]
	\includegraphics[width=0.3\textwidth]{toric_code_correction}
	\caption{QEC of a single bit-flip (top) and phase-flip (bottom) error via measuring two overlapping stabilisers. If there is at most one bit- or phase-flip error, as per this graphic, then upon measuring all the star and plaquette stabilisers, only those whose qubits are affected by the error channel will yield the $-1$ measurement outcome, the others all yielding $+1$. Such an error will affect exactly two stabilisers, whose qubit in common must have been the one affected by the respective error, which can subsequently be corrected since the type of the error and its location are known. Thus, in this example, all of the $\hat{S}_+^{(1)}$, $\hat{S}_+^{(2)}$, $\hat{S}_\square^{(1)}$ and $\hat{S}_\square^{(2)}$ stabilisers will yield $-1$ outcomes for the shown $\hat{X}$ and $\hat{Z}$ errors, whereas any of the remaining (not shown) $\hat{S}_k^{(j)}$ will yield $+1$ outcomes, which uniquely specifies where those errors took place.}\label{fig:toric_corr}	
\end{figure}

@@

\begin{figure}[htpb]
	\includegraphics[width=0.47\textwidth]{torus_paulis}
	\caption{Implementation of logical Pauli-$\hat{X}$ (\comment{which colour?}) and -$\hat{Z}$ (\comment{which colour?}) operations on a toric code qubit via the application of a chain of local Paulis. The chains must circumnavigate the torus around either axis. Any path topologically equivalent to such a circumnavigation of the torus is sufficient, enabling paths to bypass defects in the lattice.} \label{fig:toric_code_paulis}
\end{figure}

@@

Aside from the \textit{active} QoS techniques discussed until now, there is also a recently described \textit{passive} technique that requires no feedforward to operate. This technique, called \textit{unitary error averaging} \cite{MarshmanLundRohde}, is formulated specifically in the linear optical context. It is an open question whether it generalises to other models, such as conventional quantum circuits.

@@

\cite{MarshmanLundRohdeRalph} showed that by using an optical fanout\index{Fanout operation} operation, which splits a set of optical modes equally across multiple sets of modes in a type of redundant encoding\footnote{The optical fanout operation effectively maps single-photon states to W-states (Sec.~\ref{sec:W_state_prep})\index{W-states}.}, and passing each set through an independently manufactured copy of the imperfect unitary, $\tilde{U}_i$, upon performing a fan-in to recombine the modes, and post-selection on detecting all photons in the desired output modes, the output state will behave as if it had evolved through a network given by the arithmetic average of each of the imperfect copies of $\hat{U}_\mathrm{target}$,
\begin{align}
\hat{U}_\mathrm{av} = \frac{1}{M}\sum_{i=1}^M \tilde{U}_i.	
\end{align}
A schematic for the optical circuit is shown in Fig.~\ref{fig:error_av_circuit}.

\begin{figure}[htpb]
\includegraphics[width=0.47\textwidth]{unitary_error_averaging}
\caption{Protocol for error correction via unitary error averaging. Here our computation resides across \mbox{$N=2$} modes, and there are \mbox{$M=2$} redundant copies of the manufactured unitary, which straightforwardly generalises to arbitrary $M$ and $N$. A fanout operation splits the wave amplitudes from the set of $N$ input modes uniformly across $M$ sets of $N$ modes. Each set of $N$ evolves through an independent copy of the manufactured imperfect unitary, $\tilde{U}_i$. A reverse fanout operation recollects the bundles of modes. Upon post-selecting upon detecting all photons within the first $N$ modes, and none in the other ancillary modes, the state is projected into the subspace as if it had been acted upon by the arithmetic average of the imperfect unitaries. If photons are detected in the error modes, our logical state has effectively suffered photon loss and has been corrupted.} \label{fig:error_av_circuit}	
\end{figure}

Note that the protocol doesn't require that the $M$ instances of the unitary be held locally. They operate independently in parallel and could therefore be distributed, with the independent copies held by entirely different parties in distant locations (Sec.~\ref{sec:error_av_parallel}).\index{Distributed quantum computation}\index{Parallelisation}

The protocol is necessarily non-deterministic, since sometimes photons will be measured in the error modes, signalling that the output state has been projected onto an erroneous subspace. Thus, this is a heralded error correction scheme. When post-selection succeeds we have effectively evolved via the averaged operator, which statistically ought to more closely approximate $\hat{U}_\mathrm{target}$ than individual $\tilde{U}_i$.

@@

\begin{figure*}[htpb]
\includegraphics[width=\textwidth]{bloch_sphere_dyn_dec}
\caption{Bloch sphere representation of a sequence to dynamically decouple an unknown $\hat{Z}$ rotation from a qubit. (a) Blue dot represents the initial state. (b) The state undergoes an unknown $\hat{Z}(\theta)$ rotation. (c) A bit-flip ($\hat{X}$) flips the Bloch sphere upside down. (d) Waiting for the same time as before such that the same unknown $\hat{Z}$-rotation takes place, the state ends up in its initial state, independent of the $\hat{Z}$-rotation angle $\theta$, but assuming it was the same on both occasions in (b) and (d).} \label{fig:bloch_sphere_dyn_dec}	
\end{figure*}
